---
title: "README"
output: github_document
---

## Dispersion study

In the data folder, I give you the intra-day dispersion numbers for the J200 (ALSI Top 40) and J400 (Swix top 40).

Also included is the weekly and 1 and 3 monthly calculated dispersion, avg stock correlation and avg SD calcs for J200, J400, J300 and J430. This is a treasure trove of data.


```{r setup, include=FALSE}
library(rmsfuns)
library(fmxdat)
if (!require(robustbase)) install.packages("robustbase")
load_pkg(c("tidyverse", "devtools", "rugarch", "forecast", "tbl2xts", 
    "lubridate", "PerformanceAnalytics", "ggthemes"))
library(tidyverse)
library(knitr)

```


# Dispersion data 

```{r}

# Intraday dispersion last 4 years:
ID_Disp <- read_rds("data/ID_Disp.rds") %>% filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-05-29"))

ID_Disp %>% 
  ggplot() + 
  geom_line(aes(date, ID_Dispersion_W_J400)) + 
  geom_line(aes(date, ID_Dispersion_W_J200), color = "red")
  
# Intraday weighted average realized volatility:
Ivol <- bind_rows(read_rds("data/J200_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J200) %>% mutate(Idx = "J200") %>% gather(Type, Value, -date, -Idx), 
                  read_rds("data/J400_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J400) %>% mutate(Idx = "J400") %>% gather(Type, Value, -date, -Idx))

Ivol %>% filter(Type == "W_Avg_RV") %>% 
  ggplot() + 
  geom_line(aes(date, Value, color = Idx)) + 
  labs(title = "Weighted Avg Realized Volatility") + theme_bw()

# Dispersion - lower frequency
W_Dispersion <- 
  read_rds("data/Dispersion/Weekly.rds")
M_Dispersion <- 
  read_rds("data/Dispersion/Monthly.rds")

```


## Importing index returns data 

```{r}
library(tbl2xts)

# the JSE top 40 index used to create a simple return index

#TP40 <- fmxdat::SA_Indexes %>% filter(Tickers == "JSHRALTR Index") %>% 
#    mutate(SimpleRet = Price / lag(Price)-1) %>% 
#    ungroup() %>% select(date, SimpleRet) %>% tbl2xts::tbl_xts()

# locally storing the TP40 data

# saveRDS(TP40, file = "data/TP40.rds")

TP40n <- read_rds("data/Top40_new.rds")
TP40 <- read_rds("data/TP40.rds")
```

## Calculate returns with new data 15/01/21

```{r}
TP40n <- read_rds("data/Top40_new.rds")
rts <- TP40n %>% select(date, Tickers, Return) %>% spread(Tickers, Return) %>% tbl_xts()
wts <- TP40n %>% select(date, Tickers, J200_W_Adj) %>% spread(Tickers, J200_W_Adj) %>% tbl_xts()

wts[is.na(wts)] <- 0
rts[is.na(rts)] <- 0

TP40rts <- Safe_Return.portfolio(R = rts, weights = wts, 
    lag_weights = T) %>% xts_tbl() %>% rename(Returns = portfolio.returns) %>% tbl_xts()

TP40rts_w <- TP40rts %>% apply.weekly(mean)


# visualize the difference between the two returns series 

plot1 <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>% mutate(Idx = "Intraday Dispersion") %>% 
  gather(Type, Value, -date, -Idx)

plot2 <- ID_Disp %>% left_join(Ivol, by = "date") %>% filter(Idx == "J200", Type == "W_Avg_RV") %>% 
  na.omit() %>% select(date, ID_Dispersion_W_J200, Value) %>% mutate(Idx = "Realized Volatility") %>% 
  select(date, Value, Idx) %>% gather(Type, Value, -date, -Idx)

plot <- bind_rows(plot1, plot2) %>% rename(Date = date)


plotf <- plot %>% 
  ggplot() + 
  geom_line(aes(Date, Value, color = Idx)) + 
  labs(title = "Weighted Avg Realized Volatility", y = "", x = "") + theme_bw() +
  theme(legend.position=c(0.4, 0.87), legend.direction = "vertical", legend.title = element_blank(),
        legend.background = element_rect(fill="white", 
                                  size=0.5, linetype="solid", colour = "black"), legend.text = element_text(size=8)) + ggtitle("")

# save plot for tex 

saveRDS(plotf, file = "plotf")
  

xts_tbl(TP40rts) %>% left_join(xts_tbl(TP40), by = "date") %>% na.omit() %>%
  ggplot() + 
  geom_line(aes(date, Returns), color = "red") +
  geom_line(aes(date, SimpleRet))


```

# Plotting the returns data 

```{r}
# plotting the data 

Plotdata <- cbind(TP40rts, TP40rts^2, abs(TP40rts))
colnames(Plotdata) <- c("Returns", "Returns_Sqd", "Returns_Abs")

Plotdata <- Plotdata %>% xts_tbl() %>% gather(ReturnType, Returns,-date) %>%
  filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-07-31"))

ggplot(Plotdata) + geom_line(aes(x = date, y = Returns, colour = ReturnType, 
    alpha = 0.5)) + ggtitle("Return Type Persistence: J200 Index") + 
    facet_wrap(~ReturnType, nrow = 3, ncol = 1, scales = "free") + 
    guides(alpha = FALSE, colour = FALSE) + theme_bw()

```


## tests

```{r}
forecast::Acf(TP40rts, main = "ACF: Equally Weighted Return")

forecast::Acf(TP40rts^2, main = "ACF: Squared Equally Weighted Return")

forecast::Acf(abs(TP40rts), main = "ACF: Absolute Equally Weighted Return")
```

These test prove that there is conditional heteroskedasticity in the data - there is volatility is clustering. 

```{r}
Box.test(coredata(TP40rts^2), type = "Ljung-Box", lag = 12)
```


# Estimating the daily GARCH model

## Simple GARCH on returns

```{r, results='asis'}
library(rugarch)

# combining the two datasets to make sure that they line up 


comb <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>%  left_join(xts_tbl(TP40rts), by="date") %>% na.omit() %>%
  tbl_xts()

combplot <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>%  left_join(xts_tbl(TP40rts), by="date") %>%
  tbl_xts() %>% na.omit %>% apply.weekly(mean) %>% xts_tbl() %>% 
  rename("Return Dispersion" = ID_Dispersion_W_J200) %>% gather(Type, Value, -date)

# Second plot for tex proj

combplot <- combplot %>% 
  ggplot() + 
  geom_line(aes(date, Value, color = Type)) + 
  labs(title = "Weighted Avg Realized Volatility", y = "", x = "") + theme_bw() +
  theme(legend.position=c(0.4, 0.87), legend.direction = "vertical", legend.title = element_blank(),
        legend.background = element_rect(fill="white", 
                                  size=0.5, linetype="solid", colour = "black"), legend.text = element_text(size=8)) + ggtitle("")

saveRDS(combplot, file = "combplot")


# remove the NAs - temporary solution 

comb[is.na(comb)] <- 0 

colSums(is.na(comb))

fit <- comb[,2] %>% as.matrix() 


# first fit the simple model to returns 

garch1 <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

garchfit1 = ugarchfit(spec = garch1, data = fit)

kable(garchfit1@fit$matcoef, format = "html")


```

## Fitting with external regressor

```{r}
# identifying the fit and external regressor for the model then fitting it to GARCH-X

exreg <- comb[,1] %>% as.matrix()

garchx <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = exreg), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

# Now to fit the garch to the returns

garchfitx = ugarchfit(spec = garchx, data = fit)

kable(garchfitx@fit$robust.matcoef, format = "html")

# save the first two garch objects for the tex 

saveRDS(garchfitx, file = "garchfitx")
saveRDS(garchfit1, file = "garchfit1")
```

## Veiw the two conditional variance plots

```{r}


# First for the garch-x
sigmax <- sigma(garchfitx) %>% xts_tbl()
colnames(sigmax) <- c("date", "sigma")
sigmax <- sigmax %>% mutate(date = as.Date(date))


ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigmax, aes(x = date, 
    y = sigma), color = "red", size = 0.3, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch-x", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")


# now for the garch

sigma <- sigma(garchfit1) %>% xts_tbl()
colnames(sigma) <- c("date", "sigma")
sigma <- sigma %>% mutate(date = as.Date(date))

ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigma, aes(x = date, 
    y = sigma), color = "red", size = 1, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")



plot(garchfitx, which = 'all')

plot(garchfit1, which = 'all')

persistence(garchfitx)


# testing the fit 

fit.ic <- cbind(infocriteria(garchfit1),infocriteria(garchfitx)) 

colnames(fit.ic) <-c("GARCH","GARCH-X")

kable(fit.ic)

```


## Forecasting with daily data

```{r}
# forecast

garchxfor <- ugarchforecast(garchfitx, data = fit, n.ahead = 10, n.roll = 0, out.sample = 100, external.forecasts = list(mregfor=NULL, vregfor=exreg))

garchfor <- ugarchforecast(garchfit1, n.ahead = 10)


# forecast sigmas:
f1 <-as.data.frame(sigma(garchfor))

f2 <-as.data.frame(sigma(garchxfor))

series1 <- fitted(garchfor)

series2 <- fitted(garchxfor)

sigmaf <- cbind(f1, f2)

fitf <-cbind(series1, series2)

vol <- sigmaf^2

colnames(vol) <- c("GARCH", "GARCH-X")

kable(vol)

```


## Testing the forecasting accuracy for the two models

```{r}
cl = makePSOCKcluster(10)


roll = ugarchroll(garch1, fit, forecast.length = 500, refit.every = 25, 
    refit.window = "moving", window.size = 600, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

rollx = ugarchroll(garchx, fit, forecast.length = 500, refit.every = 25, 
    refit.window = "moving", window.size = 600, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

# For this, only 1-step ahead can be done automatically.
show(rollx)

report(rollx, type = "fpm")

report(roll, type = "fpm")

```

## Run an AR(1) on 

```{r}
arima(TP40, order = c(1, 0, 1))

arima(exreg, order = c(1, 0, 0))
```

# Esitmating weekly data on the GARCH model

```{r}

# The two series for the model

comb2 <- comb %>% xts_tbl() %>% select(date, Returns) %>% tbl_xts() %>% apply.weekly(mean)

combmain <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>% tbl_xts() %>% apply.weekly(mean) %>% 
  xts_tbl() %>% left_join(xts_tbl(comb2), by = "date") %>% na.omit() %>% tbl_xts()

# check na's
colSums(is.na(combmain))


fitw <- combmain[,2]
exregw <- combmain[,1]

# model weekly vol with ext reg

garchweekly <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchx2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = exregw), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchfit2 <- ugarchfit(spec = garchweekly, data = fitw)

garchfitx2 <- ugarchfit(spec = garchx2, data = fitw)

# saving the output for the tex proj

saveRDS(garchfit2, file = "garchfitw")
saveRDS(garchfitx2, file = "garchfitwx")

```

## Weekly data output
```{r}
kable(garchfit2@fit$matcoef, format = "html")
kable(garchfitx2@fit$matcoef, format = "html")

LLH <- cbind(garchfit2@fit$LLH, garchfitx2@fit$LLH)
colnames(LLH) <- c("GARCH", "GARCH-X")

kable(LLH, format = "html")

fit.ic2 <- cbind(infocriteria(garchfit2),infocriteria(garchfitx2)) 

colnames(fit.ic2) <-c("GARCH","GARCH-X")

kable(fit.ic2)

# The two models show that the garch-x has a higher maximum likelhood and 
# therefore a improved goodness of fit with the dispersion measure included 
```


## Weekly forecast vol with the two models 

```{r}
garchfx_w <- ugarchforecast(garchfitx2, n.ahead = 10)
garchf2 <- ugarchforecast(garchfit2, n.ahead = 10)

plot(garchfx_w, which = 1)
plot(garchf2, which = 1)

plot(garchfx_w, which = 3)
plot(garchf2, which = 3)

# rolling forecast

cl <- makePSOCKcluster(10)
# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

roll2 <- ugarchroll(garchweekly, fitw, forecast.length = 100, refit.every = 50, 
    refit.window = "moving", window.size = 120, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

# For this, only 1-step ahead can be done automatically.
show(roll2)


report(roll2, type = "fpm")

# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

rollxw = ugarchroll(garchx2, fitw, forecast.length = 100, refit.every = 15, 
    refit.window = "moving", window.size = 150, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

rollw = ugarchroll(garchweekly, fitw, forecast.length = 100, refit.every = 15, 
    refit.window = "moving", window.size = 150, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)


report(rollxw, type = "fpm")

report(rollw, type = "fpm")

```

# Estimating monthly data on the GARCH


```{r}
M_Dispersion <- 
  read_rds("data/Dispersion/Monthly.rds")

TP40rts_m <- TP40rts %>% apply.monthly(Return.cumulative) %>% xts_tbl()


Monthly <- M_Dispersion %>% filter(Idx == "J200_W_Adj", Freq == "1_Month") %>% left_join(TP40rts_m, by = "date") %>% 
  select(date, Dispersion_W, Returns) %>% na.omit() %>% tbl_xts() 

plot.xts(Monthly$Returns)

fitm <- Monthly[,2]
exregm <- Monthly[,1]

garchxm <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = exregm), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchm <-  ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")


garchfitx4 <- ugarchfit(spec = garchxm, data = fitm)
garchfit3 <- ugarchfit(spec = garchm, data = fitm)

kable(garchfit3@fit$matcoef, format = "html")
kable(garchfitx4@fit$matcoef, format = "html")

LLH2 <- cbind(garchfit3@fit$LLH, garchfitx4@fit$LLH)
colnames(LLH2) <- c("GARCH", "GARCH-X")

kable(LLH2, format = "html")

fit.ic3 <- cbind(infocriteria(garchfit3),infocriteria(garchfitx4)) 

colnames(fit.ic3) <-c("GARCH","GARCH-X")

kable(fit.ic3)

# save the output for the tex proj

saveRDS(garchfit3, file = "garchfitm")
saveRDS(garchfitx4, file = "garchfitmx")
```


## fit the forecasts for monthly data

```{r}
garchfx_m <- ugarchforecast(garchfitx4, n.ahead = 10)
garchfm <- ugarchforecast(garchfit3, n.ahead = 10)

plot(garchfx_m, which = 1)
plot(garchfm, which = 1)

plot(garchfx_w, which = 3)
plot(garchf2, which = 3)

# rolling forecast

cl <- makePSOCKcluster(10)
# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

rollxm = ugarchroll(garchxm, fitm, forecast.length = 50, refit.every = 5, 
    refit.window = "moving", window.size = 100, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

rollm = ugarchroll(garchm, fitm, forecast.length = 50, refit.every = 5, 
    refit.window = "moving", window.size = 100, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

report(rollxm, type = "fpm")

report(rollm, type = "fpm")

```

# Truncate the sample 

## In daily format

```{r}

RvolJ200 <- Ivol %>% filter(Idx == "J200", Type == "W_Avg_RV") %>% 
  mutate(Qlow = quantile(Value, 0.15), Qhigh = quantile(Value, 0.85)) %>% 
  mutate(HighVol = ifelse(Value > Qhigh, "High", ifelse(Value < Qlow, "Low", "Neutral")))

# make nas zero, temp solution

ID_dispJ200 <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>% na.omit() %>% 
  mutate(Qlow = quantile(ID_Dispersion_W_J200, 0.15), Qhigh = quantile(ID_Dispersion_W_J200, 0.85)) %>% 
  mutate(HighVol = ifelse(ID_Dispersion_W_J200 > Qhigh, "High", ifelse(ID_Dispersion_W_J200 < Qlow, "Low", "Neutral")))

# confusion matrix/contingency table

ID_dispJ200 %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ200, by = "date") %>% rename(RealV_vol = HighVol) %>% select(Intraday_vol, RealV_vol) %>% 
  mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         RealV_vol = factor(RealV_vol, levels = c("High","Neutral", "Low"))) %>% table() %>% kable()

#install.packages("caret")
#library(caret)

```

## In weekly format

```{r}
# Truncate the weekly sample

RvolJ200w <- Ivol %>% filter(Idx == "J200", Type == "W_Avg_RV") %>% tbl_xts() %>% 
  xts_tbl() %>% mutate(Qlow = quantile(Value, 0.15), Qhigh = quantile(Value, 0.70)) %>% 
    mutate(HighVol = ifelse(Value > Qhigh, "High", ifelse(Value < Qlow, "Low", "Neutral"))) 

# remove the nas from the sample

dispJ200w <- W_Dispersion %>% filter(Idx == "J200_W_Adj") %>% select(date, Dispersion_W) %>%
  na.omit() %>% mutate(Qlow = quantile(Dispersion_W, 0.15), Qhigh = quantile(Dispersion_W, 0.85)) %>% 
  mutate(HighVol = ifelse(Dispersion_W > Qhigh, "High", ifelse(Dispersion_W < Qlow, "Low", "Neutral")))

# confusion matrix of the different periods of volatility

dispJ200w %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ200w, by = "date") %>% rename(RealV_vol = HighVol) %>% select(Intraday_vol, RealV_vol) %>% 
  mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         RealV_vol = factor(RealV_vol, levels = c("High","Neutral", "Low"))) %>% table() %>% kable()

```


## The mean of the different dispersion vol regimes

```{r}
# daily

ID_dispJ200 %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ200, by = "date") %>% mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         HighVol = factor(HighVol, levels = c("High","Neutral", "Low"))) %>% with(tapply(Value, Intraday_vol, max)) 

# weekly

dispJ200w %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ200w, by = "date") %>% na.omit() %>%
  mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral","Low")), 
         HighVol = factor(HighVol, levels = c("High","Neutral", "Low"))) %>% 
  with(tapply(Value, Intraday_vol, mean)) %>% kable()

```

# Stratfication test

```{r}

J200dispw <- ID_Disp %>% select(date, ID_Dispersion_W_J200) %>% na.omit() %>% 
  rename(Disp = ID_Dispersion_W_J200) %>% tbl_xts() %>% apply.weekly(mean) %>% 
  xts_tbl() %>% mutate(Qlow = quantile(Disp, 0.20), Qhigh = quantile(Disp ,0.55)) %>% 
  mutate(HighVol = ifelse(Disp > Qhigh, "High", ifelse(Disp < Qlow, "Low", "Neutral")))

highdisp <- J200dispw %>% filter(HighVol == "High") %>% select(date, Disp) %>% 
  left_join(xts_tbl(comb2), by = "date")

J200dispw %>% na.omit() %>%
  ggplot() + 
  geom_line(aes(date, Disp)) + 
  geom_line(aes(date, Qlow), color = "red") +
  geom_line(aes(date, Qhigh), color = "blue") 


```


# dummy variables 

```{r}

TP40dummy <- TP40rts_w %>% xts_tbl() %>% 
  mutate(Qlow = quantile(Returns, 0.15), Qhigh = quantile(Returns, 0.75)) %>% 
  mutate(HighVol = ifelse(Returns > Qhigh, "High", ifelse(Returns < Qlow, "Low", "Neutral"))) %>%
  mutate(dummy = ifelse(HighVol=="High", 1, 0))

RvolJ200w1 <- RvolJ200w %>% select(date, Value) %>% tbl_xts()

Hdummy <- J200dispw %>%  mutate(dummy = ifelse(J200dispw$HighVol=="High", 1, 0)) %>% 
  select(date, dummy) %>% left_join(xts_tbl(TP40rts_w), by = "date") %>% na.omit() %>% 
  select(dummy) %>% as.matrix()

J200dispw %>%  mutate(dummy = ifelse(J200dispw$HighVol=="Low", 1, NA)) %>% 
  select(date, dummy) %>% left_join(xts_tbl(TP40rts_w), by = "date") %>% na.omit() %>% 
  select(Returns) %>% as.matrix() %>% abs() %>% mean()


Ndummy <- J200dispw %>%  mutate(dummyn = ifelse(J200dispw$HighVol=="Neutral", 1, 0)) %>% 
  select(date, dummyn) %>%  left_join(xts_tbl(TP40rts_w), by = "date") %>% select(dummyn)
  
Ldummy <- J200dispw %>%  mutate(dummyl = ifelse(J200dispw$HighVol=="Low", 1, 0)) %>% 
  na.omit() %>% select(dummyl) %>% as.matrix()

exregdum <- cbind(Hdummy, Ndummy, Ldummy) %>% as.matrix()


garchx3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = Hdummy), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchfitx3 <- ugarchfit(spec = garchx3, data = fitw)



kable(garchfitx3@fit$matcoef, format = "html")

kable(garchfitx3@fit$LLH, format = "html")

```


# two statified periods 

```{r}

Hdummy2 <- J200dispw %>%  mutate(dummy = ifelse(J200dispw$HighVol=="High", 1, 0)) %>% 
  left_join(xts_tbl(TP40rts_w), by = "date") %>% filter(dummy == 1) %>% select(Disp, Returns)

exreg1 <- Hdummy2[,1] %>% as.matrix()
fit1 <- Hdummy2[,2] %>% as.matrix()



garchx4 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = exreg1), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchfitx5 <- ugarchfit(spec = garchx4, data = fit1)


Ldummy2 <- J200dispw %>%  mutate(dummy = ifelse(J200dispw$HighVol=="High", 1, 0)) %>% 
  left_join(xts_tbl(TP40rts_w), by = "date") %>% filter(dummy == 0) %>% select(Disp, Returns)



exreg2 <- Ldummy2[,1] %>% as.matrix()
fit2 <- Ldummy2[,2] %>% as.matrix()


garchx5 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = exreg2), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")


garchfitx6 <- ugarchfit(spec = garchx5, data = fit2)

kable(garchfitx6@fit$matcoef, format = "html")

# save the two stratified periods


saveRDS(garchfitx5, file = "garchfitsh")
saveRDS(garchfitx6, file = "garchfitsl")


```



