---
title: "README"
output: github_document
---

## Dispersion study

In the data folder, I give you the intra-day dispersion numbers for the J200 (ALSI Top 40) and J400 (Swix top 40).

Also included is the weekly and 1 and 3 monthly calculated dispersion, avg stock correlation and avg SD calcs for J200, J400, J300 and J430. This is a treasure trove of data.



```{r}
library(tidyverse)

# Intraday dispersion last 4 years:
ID_Disp <- read_rds("data/ID_Disp.rds") %>% filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-07-31"))

ID_Disp %>% 
  ggplot() + 
  geom_line(aes(date, ID_Dispersion_W_J400)) + 
  geom_line(aes(date, ID_Dispersion_W_J200), color = "red")


  
# Intraday weighted average realized volatility:
Ivol <- bind_rows(read_rds("data/J200_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J200) %>% mutate(Idx = "J200") %>% gather(Type, Value, -date, -Idx), 
                  read_rds("data/J400_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J400) %>% mutate(Idx = "J400") %>% gather(Type, Value, -date, -Idx))

Ivol %>% filter(Type == "W_Avg_RV") %>% 
  ggplot() + 
  geom_line(aes(date, Value, color = Idx)) + 
  labs(title = "Weighted Avg Realized Volatility") + theme_bw()

# Dispersion - lower frequency
W_Dispersion <- 
  read_rds("data/Dispersion/Weekly.rds")
M_Dispersion <- 
  read_rds("data/Dispersion/Monthly.rds")

```


## Importing index returns data 

```{r}
library(tbl2xts)

# the JSE top 40 index used to create a simple return index

view(fmxdat::SA_Indexes)

TP40 <- fmxdat::SA_Indexes %>% filter(Tickers == "JSHR40TR Index") %>% 
    mutate(SimpleRet = Price / lag(Price)-1) %>% 
    ungroup() %>% select(date, SimpleRet) %>% tbl2xts::tbl_xts()

Plotdata <- cbind(TP40, TP40^2, abs(TP40))
colnames(Plotdata) <- c("Returns", "Returns_Sqd", "Returns_Abs")

Plotdata <- Plotdata %>% xts_tbl() %>% gather(ReturnType, Returns,-date) %>%
  filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-07-31"))

ggplot(Plotdata) + geom_line(aes(x = date, y = Returns, colour = ReturnType, 
    alpha = 0.5)) + ggtitle("Return Type Persistence: TOP40TR Index") + 
    facet_wrap(~ReturnType, nrow = 3, ncol = 1, scales = "free") + 
    guides(alpha = FALSE, colour = FALSE) + theme_bw()

```


# Estimating the GARCH

```{r}
library(rugarch)

# combining the two datasets to make sure that they line up 

comb <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>%  left_join(xts_tbl(TP40), by="date") %>%
  tbl_xts() 

# plot dispersion against returns

comb %>% xts_tbl() %>% 
  ggplot() + 
  geom_line(aes(date, ID_Dispersion_W_J400), color = "steel blue") + 
  geom_line(aes(date, SimpleRet), color = "red")

# remove the NAs - temporary solution 

comb[is.na(comb)] <- 0 

colSums(is.na(comb))

fit <- comb[,2]


# first fit the simple model to returns 

garch1 <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

garchfit1 = ugarchfit(spec = garch1, data = fit)

print(garchfit1)

# identifying the fit and external regressor for the model then fitting it to GARCH-X

exreg <- comb[,1]

garchx <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = exreg), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

# Now to fit the garch to the returns

garchfitx = ugarchfit(spec = garchx, data = fit)

garchfitx
```


## Veiw the two conditional variance plots

```{r}


# First for the garch-x
sigmax <- sigma(garchfitx) %>% xts_tbl()
colnames(sigmax) <- c("date", "sigma")
sigmax <- sigmax %>% mutate(date = as.Date(date))


ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigmax, aes(x = date, 
    y = sigma), color = "red", size = 2, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")


# now for the garch

sigma <- sigma(garchfit1) %>% xts_tbl()
colnames(sigma) <- c("date", "sigma")
sigma <- sigma %>% mutate(date = as.Date(date))

ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigma, aes(x = date, 
    y = sigma), color = "red", size = 2, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")


plot(garchfitx, which = 3)

plot(garchfit1, which = 3)


# testing the fit 

infocriteria(garchfit1)

infocriteria(garchfitx)

```

## forecast vol with the two models 

```{r}
garchfx <- ugarchforecast(garchfitx, n.ahead = 30)
garchf <- ugarchforecast(garchfit1, n.ahead = 5)

plot(garchfx, which = 1)
plot(garchf, which = 1)



# rolling forecast

cl <- makePSOCKcluster(10)
spec <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution = "norm")
# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

roll <- ugarchroll(spec, fit, forecast.length = 500, refit.every = 50, 
    refit.window = "moving", window.size = 1000, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

# For this, only 1-step ahead can be done automatically.
show(roll)


report(roll, type = "fpm")

```


