---
title: "README"
output: github_document
---

## Dispersion study

In the data folder, I give you the intra-day dispersion numbers for the J200 (ALSI Top 40) and J400 (Swix top 40).

Also included is the weekly and 1 and 3 monthly calculated dispersion, avg stock correlation and avg SD calcs for J200, J400, J300 and J430. This is a treasure trove of data.


```{r setup, include=FALSE}
library(rmsfuns)
library(fmxdat)
if (!require(robustbase)) install.packages("robustbase")
load_pkg(c("tidyverse", "devtools", "rugarch", "forecast", "tbl2xts", 
    "lubridate", "PerformanceAnalytics", "ggthemes"))
library(tidyverse)
library(knitr)
```


```{r}

# Intraday dispersion last 4 years:
ID_Disp <- read_rds("data/ID_Disp.rds") %>% filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-07-31"))

ID_dispw <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>% tbl_xts() %>% apply.weekly(mean)

ID_Disp %>% 
  ggplot() + 
  geom_line(aes(date, ID_Dispersion_W_J400)) + 
  geom_line(aes(date, ID_Dispersion_W_J200), color = "red")


  
# Intraday weighted average realized volatility:
Ivol <- bind_rows(read_rds("data/J200_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J200) %>% mutate(Idx = "J200") %>% gather(Type, Value, -date, -Idx), 
                  read_rds("data/J400_IVol.rds") %>% select(date, Avg_RV, W_Avg_RV = W_Avg_RV_J400) %>% mutate(Idx = "J400") %>% gather(Type, Value, -date, -Idx))

Ivol %>% filter(Type == "W_Avg_RV") %>% 
  ggplot() + 
  geom_line(aes(date, Value, color = Idx)) + 
  labs(title = "Weighted Avg Realized Volatility") + theme_bw()

# Dispersion - lower frequency
W_Dispersion <- 
  read_rds("data/Dispersion/Weekly.rds")
M_Dispersion <- 
  read_rds("data/Dispersion/Monthly.rds")

```


## Importing index returns data 

The returns data used to construct the 

```{r}
library(tbl2xts)

# the JSE top 40 index used to create a simple return index

#TP40 <- fmxdat::SA_Indexes %>% filter(Tickers == "JSHRALTR Index") %>% 
#    mutate(SimpleRet = Price / lag(Price)-1) %>% 
#    ungroup() %>% select(date, SimpleRet) %>% tbl2xts::tbl_xts()

# locally storing the TP40 data

# saveRDS(TP40, file = "data/TP40.rds")

TP40 <- read_rds("data/TP40.rds")

# plotting the data 

Plotdata <- cbind(TP40, TP40^2, abs(TP40))
colnames(Plotdata) <- c("Returns", "Returns_Sqd", "Returns_Abs")

Plotdata <- Plotdata %>% xts_tbl() %>% gather(ReturnType, Returns,-date) %>%
  filter(date >= as.Date("2016-07-29") & date <= as.Date("2020-07-31"))

ggplot(Plotdata) + geom_line(aes(x = date, y = Returns, colour = ReturnType, 
    alpha = 0.5)) + ggtitle("Return Type Persistence: TOP40TR Index") + 
    facet_wrap(~ReturnType, nrow = 3, ncol = 1, scales = "free") + 
    guides(alpha = FALSE, colour = FALSE) + theme_bw()

```


## tests

```{r}
forecast::Acf(TP40, main = "ACF: Equally Weighted Return")

forecast::Acf(TP40^2, main = "ACF: Squared Equally Weighted Return")

forecast::Acf(abs(TP40), main = "ACF: Absolute Equally Weighted Return")
```

These test prove that there is conditional heteroskedasticity in the data - there is volatility is clustering. 

```{r}
Box.test(coredata(TP40^2), type = "Ljung-Box", lag = 12)
```


# Estimating the GARCH

## Simple GARCH on returns

```{r, results='asis'}
library(rugarch)

# combining the two datasets to make sure that they line up 

comb <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>%  left_join(xts_tbl(TP40), by="date") %>%
  tbl_xts() 

# plot dispersion against returns

comb %>% xts_tbl() %>% 
  ggplot() + 
  geom_line(aes(date, ID_Dispersion_W_J400), color = "steel blue") + 
  geom_line(aes(date, SimpleRet), color = "red")

# remove the NAs - temporary solution 

comb[is.na(comb)] <- 0 

colSums(is.na(comb))

fit <- comb[,2]


# first fit the simple model to returns 

garch1 <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

garchfit1 = ugarchfit(spec = garch1, data = fit)

kable(garchfit1@fit$matcoef, format = "html")

kable(garchfit1@fit$robust.matcoef, format = "html")

```

## Fitting with external reg

```{r}
# identifying the fit and external regressor for the model then fitting it to GARCH-X

exreg <- comb[,1]

garchx <- ugarchspec(variance.model = list(model = c("sGARCH", 
    "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(1, 
    1), external.regressors = exreg), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = c("norm", "snorm", "std", "sstd", "ged","sged", "nig", "ghyp", "jsu")[1])

# Now to fit the garch to the returns

garchfitx = ugarchfit(spec = garchx, data = fit)

kable(garchfitx@fit$matcoef, format = "html")

kable(garchfitx@fit$robust.matcoef, format = "html")

# forecast

garchxfor <- ugarchforecast(garchfitx, data = NULL, n.ahead = 10, n.roll
                        = 0, out.sample = 100, external.forecasts = list(mregfor=NULL, vregfor=exreg))

garchfor <- ugarchforecast(garchfit1, n.ahead = 10)


# forecast sigmas:
f1 <-as.data.frame(sigma(garchfor))

f2 <-as.data.frame(sigma(garchxfor))

series1 <- fitted(garchfor)

series2 <- fitted(garchxfor)

sigmaf <- cbind(f1, f2)

fitf <-cbind(series1, series2)

vol <- sigmaf^2

colnames(vol) <- c("GARCH", "GARCH-X")

kable(vol)

```

## compare forecasts

## Veiw the two conditional variance plots

```{r}


# First for the garch-x
sigmax <- sigma(garchfitx) %>% xts_tbl()
colnames(sigmax) <- c("date", "sigma")
sigmax <- sigmax %>% mutate(date = as.Date(date))


ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigmax, aes(x = date, 
    y = sigma), color = "red", size = 1, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch-x", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")


# now for the garch

sigma <- sigma(garchfit1) %>% xts_tbl()
colnames(sigma) <- c("date", "sigma")
sigma <- sigma %>% mutate(date = as.Date(date))

ggplot() + geom_line(data = Plotdata %>% filter(ReturnType == 
    "Returns_Sqd") %>% select(date, Returns) %>% unique %>% mutate(Returns = sqrt(Returns)), 
    aes(x = date, y = Returns)) + geom_line(data = sigma, aes(x = date, 
    y = sigma), color = "red", size = 1, alpha = 0.8) + theme_bw() + 
    # scale_y_continuous(limits = c(0, 0.35)) +
labs(title = "Comparison: Returns Sigma vs Sigma from Garch", 
    subtitle = "Note the smoothing effect of garch, as noise is controlled for.", 
    x = "", y = "Comparison of estimated volatility")



plot(garchfitx, which = 'all')

plot(garchfit1, which = 'all')


# testing the fit 

fit.ic <- cbind(infocriteria(garchfit1),infocriteria(garchfitx)) 

colnames(fit.ic) <-c("GARCH","GARCH-X")

kable(fit.ic)

```




## forecast vol with the two models 

```{r}
garchfx <- ugarchforecast(garchfitx, n.ahead = 10)
garchf <- ugarchforecast(garchfit1, n.ahead = 10)

plot(garchfx, which = 1)
plot(garchf, which = 1)

plot(garchfx, which = 3)
plot(garchf, which = 3)

# rolling forecast

cl <- makePSOCKcluster(10)
# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

roll <- ugarchroll(garch1, fit, forecast.length = 500, refit.every = 50, 
    refit.window = "moving", window.size = 1000, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

# For this, only 1-step ahead can be done automatically.
show(roll)


report(roll, type = "fpm")

# Thus the model spec is a ARIMA(1,1,0)-GJRGARCH(1,1), with
# normal distribution

rollx <- ugarchroll(garchx, fit, forecast.length = 500, refit.every = 50, 
    refit.window = "moving", window.size = 1000, calculate.VaR = TRUE, 
    VaR.alpha = c(0.01, 0.05), keep.coef = TRUE, cluster = cl)

# For this, only 1-step ahead can be done automatically.
show(rollx)

report(rollx, type = "fpm")

report(roll, type = "fpm")

```



## Run an AR(1) on 

```{r}
arima(TP40, order = c(1, 0, 1))

arima(exreg, order = c(1, 0, 0))
```


## Truncate the sample in daily data

```{r}

RvolJ400 <- Ivol %>% filter(Idx == "J400", Type == "W_Avg_RV") %>% tbl_df() %>% 
  mutate(Qlow = quantile(Value, 0.15), Qhigh = quantile(Value, 0.85)) %>% 
  mutate(HighVol = ifelse(Value > Qhigh, "High", ifelse(Value < Qlow, "Low", "Neutral")))

# make nas zero, temp solution

ID_dispJ400 <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>% na.omit() %>% 
  mutate(Qlow = quantile(ID_Dispersion_W_J400, 0.15), Qhigh = quantile(ID_Dispersion_W_J400, 0.85)) %>% 
  mutate(HighVol = ifelse(ID_Dispersion_W_J400 > Qhigh, "High", ifelse(ID_Dispersion_W_J400 < Qlow, "Low", "Neutral")))

# confusion matrix/contingency table

ID_dispJ400 %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ400, by = "date") %>% rename(RealV_vol = HighVol) %>% select(Intraday_vol, RealV_vol) %>% 
  mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         RealV_vol = factor(RealV_vol, levels = c("High","Neutral", "Low"))) %>% table() %>% kable()

#install.packages("caret")
#library(caret)

```

## truncate the sample in weekly format

```{r}
# Truncate the weekly sample

RvolJ400w <- Ivol %>% filter(Idx == "J400", Type == "W_Avg_RV") %>% tbl_xts() %>% apply.weekly(mean) %>% 
  xts_tbl() %>% mutate(Qlow = quantile(Value, 0.15), Qhigh = quantile(Value, 0.85)) %>% 
    mutate(HighVol = ifelse(Value > Qhigh, "High", ifelse(Value < Qlow, "Low", "Neutral"))) 

# remove the nas from the sample

ID_dispJ400w <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>% na.omit() %>% tbl_xts() %>% apply.weekly(mean) %>%
  xts_tbl() %>% mutate(Qlow = quantile(ID_Dispersion_W_J400, 0.15), Qhigh = quantile(ID_Dispersion_W_J400, 0.85)) %>% 
  mutate(HighVol = ifelse(ID_Dispersion_W_J400 > Qhigh, "High", ifelse(ID_Dispersion_W_J400 < Qlow, "Low", "Neutral")))

# confusion matrix of the different periods of volatility

ID_dispJ400w %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ400w, by = "date") %>% rename(RealV_vol = HighVol) %>% select(Intraday_vol, RealV_vol) %>% 
  mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         RealV_vol = factor(RealV_vol, levels = c("High","Neutral", "Low"))) %>% table() %>% kable()

```


## The mean of the different dispersion vol regimes

```{r}
ID_dispJ400 %>% select(date, HighVol) %>% rename(Intraday_vol = HighVol) %>% 
  left_join(RvolJ400, by = "date") %>% mutate(Intraday_vol = factor(Intraday_vol, levels = c("High","Neutral", "Low")), 
         HighVol = factor(HighVol, levels = c("High","Neutral", "Low"))) %>% with(tapply(Value, Intraday_vol, mean))

```

## Lets try and fit weekly data to garch 

```{r}

# The two series for the model

comb2 <- comb %>% xts_tbl() %>% select(date, SimpleRet) %>% tbl_xts() %>% apply.weekly(mean)

combmain <- ID_Disp %>% select(date, ID_Dispersion_W_J400) %>% tbl_xts() %>% apply.weekly(mean) %>% 
  xts_tbl() %>% left_join(xts_tbl(comb2), by = "date") %>% na.omit() %>% tbl_xts() 

# check na's
colSums(is.na(combmain))


fitw <- combmain[,2]
exregw <- combmain[,1]

# model weekly vol with ext reg

garchweekly <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = NULL), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchx2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 
    1), external.regressors = exregw), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
    distribution.model = "norm")

garchfit2 <- ugarchfit(spec = garchweekly, data = fitw)

garchfitx2 <- ugarchfit(spec = garchx2, data = fitw)

```

## Weekly data normal
```{r}
kable(garchfit2@fit$matcoef, format = "html")
kable(garchfit2@fit$robust.matcoef, format = "html")
```


## Weekly data ext reg
```{r}
kable(garchfitx2@fit$matcoef, format = "html")
kable(garchfitx2@fit$robust.matcoef, format = "html")
```




